### 2025-07-22 modern-portfolio-theory.qmd
20250721 - diversification

Another important idea from modern portfolio theory is that, if you want to achieve higher returns, you may be able to by accepting additional—and the right combination of—risk.
In general, risk is positively correlated with return.
That is, receiving higher returns generally requires taking on additional risk—at least as long as we stay along the [efficient frontier](#sec-efficientFrontier), described next.

>>>>

Another important idea from modern portfolio theory is that, if you want to achieve higher returns, you may be able to by accepting additional—and the right combination of—risk.
In general, risk is positively correlated with return.
That is, receiving higher returns generally requires taking on additional risk—at least as long as we stay along the [efficient frontier](#sec-efficientFrontier), described next.
Diversification, by contrast, can limit your upside (by also limiting your downside).
In other words, if your goal is to win your fantasy league, you may need to be willing to carry additional risk (e.g., drafting a Quarterback and Wide Receiver from the same team), knowing full well the possibility that it will not work out as predicted.
However, winning a fantasy football league requires multiple predictions to work out as expected, which can benefit from situations where the bets were correlated.
If you are going to lean into variability, you might take several steps: a) draft multiple players from the same team (aka "[stacking](#sec-stacking)"; e.g., Quarterback and Wide Receiver) or go all in on a high-powered offense and b) target high-risk, high-reward players (i.e., players with a high "ceiling"), such as rookies, sleepers, and players coming off injuries, trades, and suspensions.
